Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-23 Methods-and-Results.Rmd
topic model conclusion added

Beyond the individual results of three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results. In particular, we aim to gain a broader picture of the individual results by considering them jointly, and we leverage the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.

@@

Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature. Something about need theories/models plus our own review article.

>>>>

Beyond the individual results of the three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results. In particular, we aim to gain a broader picture of the individual results by considering them jointly, and we leverage the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.

@@

Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}.
